---
title: "Description"
author: "Osama Jamil"
date: "27/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rlang)
library(stringr)
```

## Fortran Wrapper

This is a simple wrapper, which converts a fortran function and outputs the function to global environment,
This function has been created on MAC OSx and assumes gFortran Compiler is installed. This wrapper will not work with recursive fortran subroutines

```{r Fortran Function}
Fortran_Execute <- function(Fortran_Code)
{
  Fortran_Code_per_Line <- str_split(Fortran_Code, "\n")[[1]]
  routine_name <- Fortran_Code_per_Line[1]
  routine_name
  routine_name <- str_split_fixed(routine_name, " ",3)[2]
  routine_name <- trimws(routine_name)
  routine_name <- gsub("\\s*\\([^\\)]+\\)","",routine_name)
  Variable_def <- str_split_fixed(Fortran_Code_per_Line[1], "[(]",2)[2]
  Variable_def <- str_remove_all(string = Variable_def, pattern = "[)]")
  Variable_def
  Variable_def <- unlist(stringr::str_split(Variable_def,","))
  Variable_def
  Variable_def <- trimws(Variable_def)
  Variable_def
  
  location_of_types <- grep("integer|double",Fortran_Code_per_Line)
  input_Variables <- Variable_def
  
  for(i in 1:length(location_of_types))
  { #i=3
    Variable_def_type <- str_remove_all(str_split(Fortran_Code_per_Line[location_of_types[i]], " ", simplify = TRUE), ",")
    Variable_def_type <- gsub("\\s*\\([^\\)]+\\)","",Variable_def_type)
    Locations <- match(Variable_def_type,input_Variables)[!is.na(match(Variable_def_type,input_Variables))]
    input_Variables[Locations] <- Variable_def_type[1]
  }
  input_Variables
  
  
  current <- getwd()
  setwd("~/")
  writeLines(Fortran_Code, paste0(routine_name,".f90"))
  system(paste0("gfortran -c ",routine_name,".f90"))
  system(paste0("gfortran -shared -o ",routine_name,".so ",routine_name,".o"))
  dyn.load(paste0(routine_name,".so"))
  setwd(current)
  #if(length(Variable_def))
  #{
    #.Fortran("facto",n=as.integer(5),answer=as.integer(1))
  #  Function_Path <- paste0(".Fortran(", "'",routine_name,"'", ")")
  #}
  for(i in 1:length(input_Variables)){
    if(i == 1){
      Variables <- paste0("alist(num",i,"=")
      Function_Path <- 
        paste0(".Fortran(", "'",routine_name,"'",",",Variable_def[i],"=as.", input_Variables[i], "(num",i,")")
    }else{
      Function_Path <- paste0(Function_Path,",",Variable_def[i],"=as.", input_Variables[i], "(num",i,")")
      Variables <- paste0(Variables,",","num",i,"=")
    }
  }
  Function_Path <- paste0(Function_Path, ")")
  Variables <-  paste0(Variables, ")")
  #.Fortran("facto",n=as.integer(5),answer=as.integer(1))
  #Function_Path <- paste0(".Fortran(", "'",routine_name,"'", ")")
  #assign(routine_name,function()
  #{
  #  eval(parse(text = Function_Path))
  #}, envir = .GlobalEnv)
  #return(paste0(".Fortran(", "'",routine_name,"'", ")"))
  assign(routine_name, envir = .GlobalEnv,
         new_function(eval(parse(text = Variables)), quote(eval(parse(text = Function_Path)))))
  return(Function_Path)
}
```

## Fortran Code

The function simply reads the code from a variabe in our situation we'll be using a sample Fortran code facto which is mentioned at <https://www.r-bloggers.com/fortran-and-r-speed-things-up/>

```{r Facto}
Fortran_Code <- "subroutine facto(n,answer)
integer n, answer, i

answer = 1
do 100 i = 2,n
answer = answer * i
100   continue 

end"
```

## Execution

Simply run the function, and wrapper will output the function with exact name which is mentioned in the subroutine

```{r}
Fortran_Execute(Fortran_Code)
```

# Running the newly created function

Simply run the newly created function as you'd in R
```{r}
facto(5,1)
```

